Impact of Context in the Perception of a Robot

### 2015-06-15 main.tex
Fixed citation style + resize figures for single column

\rightheader{Impact of Context in the Perception of  a Robot}   % This should be the title, or a shortened version of the title if your title is long.
\leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
\title{Insights on the Impact of Context in the Perception of a Robot}

@@

Robotics researchers often tend to consider that anthropomorphism only describes
a static set of human-like features of a robot (like its shape, its speech
capabilities, facial expressions, etc.). We refer to these characteristics as
the \emph{anthropomorphic design} of the
robot~\cite{fink_anthropomorphism_2012}, and propose that
\emph{anthropomorphism} in general refers to a \emph{social phenomenon} that
emerges from the (real or imagined) interaction between a non-human agent (a
robot in our case) and a human~\cite{persson_anthropomorphism_2000}.  According
to~\cite{epley_when_2008}, anthropomorphism includes the human perception of
emotional states, motivations, intentions in the non-human agent, and tends to
ascribe those qualities to it. As such, the \textbf{dynamic and socio-cognitive
dimensions of anthropomorphism are essential to understand the complex bonds
that human users build with artificial agents such as
robots}~\cite{lemaignan2014dynamics}, and, even further, we postulate that
anthropomorphism can therefore be considered as a useful \emph{proxy} to these
intricate psychological bonds. This article aims at advancing our understanding
of this phenomenon \textbf{by evidencing the impact of the cognitive
presuppositions implied by the context of the interaction}.

The study of context in HRI is not new. \textit{Context of use} is defined by
the ISO as \textit{``users, tasks, equipment (hardware, software and materials),
and the physical and social environments in which a product is used''}, and
accordingly, there are various aspects that can impact how a robot is
experienced. The real or imagined \textit{purpose} of a robot, including the
application context in which it is typically used (\eg office environment, home,
rehabilitation center, public space, \etc) as well as the task context (\eg
serious or playful task; composition of human-robot team; number of users) and
the (social) role in which the robot is used / experienced are taken into
account. Generally, when the context of use of a robot is social, entertaining
or playful, it will enhance anthropomorphism, compared to when the context is a
routine or focused serious task (security, rescue, \etc).
\cite{joosse_what_2013} showed, for instance, that when the same robot ({\sc
nao}) was used in a different task context (cleaning task \vs tour guide), users
ascribed different personalities to the robot. \cite{goetz_cooperation_2002}
revealed a link between a robot's context of use and people's perception of the
robot: the authors found that people prefer a serious robot for serious tasks
and a less serious robot for more playful tasks. \cite{kaplan_free_2000}
discussed the role of uselessness in the design of robots. The author argues
that artificial pets like AIBO have no real purpose, in a sense that they do not
provide any kind of service or, in other words, \textit{``they are not doing
what you tell them to do''} and \textit{``they might refuse the order of its
owner''}. It may be this very aspect that increases people's tendency to
anthropomorphize the robot. According to Kaplan, it is in our daily use language
that we tend to attribute intentions to devices that are not doing their job
well.

@@

\paragraph{Measuring anthropomorphism} Measuring anthropomorphism raises
interesting methodological challenges, if only because people's perception of
robots change over the duration of their interaction with the
robots~\cite{lemaignan2014dynamics}. Takayama discusses the effects of these
changes~\cite{takayama_perspectives_2012} and differentiates between what she
calls an \emph{in-the-moment} and a \emph{reflective} perspective on agency: an
\emph{in-the-moment} perspective would refer to one's most immediate
response/sense in a given situation, while a \emph{reflective} perspective would
indicate one's reaction/sense of a situation based on a more in-depth
consideration and contemplation.  In the first phase of interaction with a
non-human agent (a robot in our case), people might respond ``mindlessly''
instead of responding consciously~\cite{nass_machines_2000}, and only after what
is called the \emph{familiarization} period, one might respond in a more
reflective manner instead of an in-the-moment reaction: Reeves
\etal~\cite{reeves_media_1996} showed for instance that subjects interacting
with technologies in ways close to how they would behave towards people, would
deny any human-like interaction in a post-hoc questionnaire, illustrating this
reflective perspective.

Yet, most of the experiments that investigate anthropomorphism in HRI are based
on post-interaction, closed questionnaires or rating scales.  The Godspeed
questionnaire~\cite{bartneck_measurement_2008}, and in particular, its subpart
focused on anthropomorphism, is the main validated questionnaire to assess
anthropomorphism. On 5 point semantic differential scales, people are asked to
rate the following constructs: fake \vs natural, machinelike \vs humanlike,
unconscious \vs conscious, artificial \vs lifelike, moving rigidly \vs moving
elegantly. Because the concept of ``human-likeness'' itself is complex and
abstract, Kahn \etal~\cite{kahn_jr._robotic_2006} suggest to ask for more
concrete constructs that are typical or unique of the concept of
``human-likeness'', and Ruijten \etal~\cite{ruijten_introducing_2014} propose
for instance a 25-item questionnaire to measure various concrete aspects of
human-likeness. Other researchers~\cite{zlotowski2014dimensions,salem2015would}
also applied a two-dimensional scale measuring \emph{Human Nature} and
\emph{Uniquely Human} traits of robots, based on an original proposal by Haslam
\etal~\cite{haslam2008attributing}.

@@

\begin{figure}
    \centering
    \subfigure[\emph{Picking} task, robot condition]{
        \includegraphics[height=3cm]{stimulus-robot-toys}
    }
    \subfigure[\emph{Picking} task, human condition]{
        \includegraphics[height=3cm]{stimulus-human-toys}
    }

    \subfigure[\emph{Sound} task, robot condition]{
        \includegraphics[height=3cm]{stimulus-robot-noise}
    }
    \subfigure[\emph{Sound} task, human condition]{
        \includegraphics[height=3cm]{stimulus-human-noise}
    }

@@

\begin{figure}
    \centering
    \subfigure[\emph{Picking} task, robot condition]
    {\includegraphics[width=0.8\columnwidth]{aoi-robot}\label{fig:aoi-toys}}

    \subfigure[\emph{Sound} task, human condition]
    {\includegraphics[width=0.8\columnwidth]{aoi-human}\label{fig:aoi-noise}}

>>>>

\rightheader{Impact of Context in the Perception of a Robot}   % This should be the title, or a shortened version of the title if your title is long.
\leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
\title{Impact of Context in the Perception of a Robot}

@@

Robotics researchers often tend to consider that anthropomorphism only describes
a static set of human-like features of a robot (like its shape, its speech
capabilities, facial expressions, etc.). We refer to these characteristics as
the \emph{anthropomorphic design} of the
robot~\citep{fink_anthropomorphism_2012}, and propose that
\emph{anthropomorphism} in general refers to a \emph{social phenomenon} that
emerges from the (real or imagined) interaction between a non-human agent (a
robot in our case) and a human~\citep{persson_anthropomorphism_2000}.  According
to~\citet{epley_when_2008}, anthropomorphism includes the human perception of
emotional states, motivations, intentions in the non-human agent, and tends to
ascribe those qualities to it. As such, the \textbf{dynamic and socio-cognitive
dimensions of anthropomorphism are essential to understand the complex bonds
that human users build with artificial agents such as
robots}~\citep{lemaignan2014dynamics}, and, even further, we postulate that
anthropomorphism can therefore be considered as a useful \emph{proxy} to these
intricate psychological bonds. This article aims at advancing our understanding
of this phenomenon \textbf{by evidencing the impact of the cognitive
presuppositions implied by the context of the interaction}.

The study of context in HRI is not new. \textit{Context of use} is defined by
the ISO as \textit{``users, tasks, equipment (hardware, software and materials),
and the physical and social environments in which a product is used''}, and
accordingly, there are various aspects that can impact how a robot is
experienced. The real or imagined \textit{purpose} of a robot, including the
application context in which it is typically used (\eg office environment, home,
rehabilitation center, public space, \etc) as well as the task context (\eg
serious or playful task; composition of human-robot team; number of users) and
the (social) role in which the robot is used / experienced are taken into
account. Generally, when the context of use of a robot is social, entertaining
or playful, it will enhance anthropomorphism, compared to when the context is a
routine or focused serious task (security, rescue, \etc).
\citet{joosse_what_2013} showed, for instance, that when the same robot ({\sc
nao}) was used in a different task context (cleaning task \vs tour guide), users
ascribed different personalities to the robot. \citet{goetz_cooperation_2002}
revealed a link between a robot's context of use and people's perception of the
robot: the authors found that people prefer a serious robot for serious tasks
and a less serious robot for more playful tasks. \citet{kaplan_free_2000}
discussed the role of uselessness in the design of robots. The author argues
that artificial pets like AIBO have no real purpose, in a sense that they do not
provide any kind of service or, in other words, \textit{``they are not doing
what you tell them to do''} and \textit{``they might refuse the order of its
owner''}. It may be this very aspect that increases people's tendency to
anthropomorphize the robot. According to Kaplan, it is in our daily use language
that we tend to attribute intentions to devices that are not doing their job
well.

@@

\paragraph{Measuring anthropomorphism} Measuring anthropomorphism raises
interesting methodological challenges, if only because people's perception of
robots change over the duration of their interaction with the
robots~\citep{lemaignan2014dynamics}. \citet{takayama_perspectives_2012}
discusses the effects of these changes and differentiates between what she calls
an \emph{in-the-moment} and a \emph{reflective} perspective on agency: an
\emph{in-the-moment} perspective would refer to one's most immediate
response/sense in a given situation, while a \emph{reflective} perspective would
indicate one's reaction/sense of a situation based on a more in-depth
consideration and contemplation.  In the first phase of interaction with a
non-human agent (a robot in our case), people might respond ``mindlessly''
instead of responding consciously~\citep{nass_machines_2000}, and only after
what is called the \emph{familiarization} period, one might respond in a more
reflective manner instead of an in-the-moment reaction: \citet{reeves_media_1996} showed for instance that subjects interacting
with technologies in ways close to how they would behave towards people, would
deny any human-like interaction in a post-hoc questionnaire, illustrating this
reflective perspective.

Yet, most of the experiments that investigate anthropomorphism in HRI are based
on post-interaction, closed questionnaires or rating scales.  The Godspeed
questionnaire~\citep{bartneck_measurement_2008}, and in particular, its subpart
focused on anthropomorphism, is the main validated questionnaire to assess
anthropomorphism. On 5 point semantic differential scales, people are asked to
rate the following constructs: fake \vs natural, machinelike \vs humanlike,
unconscious \vs conscious, artificial \vs lifelike, moving rigidly \vs moving
elegantly. Because the concept of ``human-likeness'' itself is complex and
abstract, \citet{kahn_jr._robotic_2006} suggest to ask for more concrete
constructs that are typical or unique of the concept of ``human-likeness'', and
\citet{ruijten_introducing_2014} propose for instance a 25-item questionnaire to
measure various concrete aspects of human-likeness. Other
researchers~\citep{zlotowski2014dimensions,salem2015would} also applied a
two-dimensional scale measuring \emph{Human Nature} and \emph{Uniquely Human}
traits of robots, based on an original proposal by \citet{haslam2008attributing}.

@@

\begin{figure}
    \centering
    \subfigure[\emph{Picking} task, robot condition]{
        \includegraphics[height=5cm]{stimulus-robot-toys}
    }
    \subfigure[\emph{Picking} task, human condition]{
        \includegraphics[height=5cm]{stimulus-human-toys}
    }

    \subfigure[\emph{Sound} task, robot condition]{
        \includegraphics[height=5cm]{stimulus-robot-noise}
    }
    \subfigure[\emph{Sound} task, human condition]{
        \includegraphics[height=5cm]{stimulus-human-noise}
    }

@@

\begin{figure}
    \centering
    \subfigure[\emph{Picking} task, robot condition]
    {\includegraphics[height=5cm]{aoi-robot}\label{fig:aoi-toys}}
    \subfigure[\emph{Sound} task, human condition]
    {\includegraphics[height=5cm]{aoi-human}\label{fig:aoi-noise}}
